---
author: Elliot Martin
title: Bioinformatician
format:
  classic-cv-pdf: default
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Bioinformatician
    left: SOPHiA Genetics
    right: elliotmartin92@gmail.com
  - title: Field
    left: Bioinformatics, Software Engineering, Data Science
    right: github.com/elliotmartin92
execute:
  echo: false
---

```{r setup}
#| warning: false
library(magrittr)
```

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

* Developed dozens of custom NGS pipelines for renowned hospitals and testing labs

* Aided PI to achieve over $2,000,000 in NIH grant funding by establishing bioinformatics pipelines
to facilitate the research of dozens of team-members

* Spearheaded a productive multi-year research project, managing and effectively communicating
with several team-members from different disciplines


# Experience


```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Bioinformatician", "SOPHiA Genetics", "Apr. 2022 - Present",
    "Transparent Social Analytics, Department of Computational Social Science", c("Coordination of a project to build an Open Science platform with reusable code and tutorials", "Research on Open Science Practices", "Implementation of tools to enhance reproducibility and facilitate research with digital data in R"),
    "Graduate Assistant", "University of Manchester", "Sep. 2018 - Feb. 2022",
    "Sociology Department", c("Research on Disinformation on Social Media", "Analyses of large scale and unstructured data sets with R, Python and Bash"),
    "Post Doctoral Researcher", "ETH Zurich", "Nov. 2017 - Aug. 2018", "Chair of Social Networks", c("Developing new methods to analyze social networks", "Implementing methods in libraries", "Gathering and analyzing large datsets from Social Media APIs"),
    "Post Doctoral Researcher", "University of Konstanz", "Oct. 2015 - Oct. 2017", "Department of Computer & Information Science", c("Developing new methods to analyze social networks", "Implementing methods in libraries", "Webscraping and harmonizing a large corpus of football data"),
    "Ph.D. Candidate", "University of Konstanz", "Nov. 2012 - Sep. 2015", "Department of Computer & Information Science", c("Developing new methods to analyze social networks", "Implementing methods in libraries")
) %>%
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Ph.D. in Computer Science", "University of Konstanz", "Konstanz, Germany", "Nov. 2012 - Sep. 2015", c("Thesis: A Positional Approach for Network Centrality", "Developed and implemented new methods to assess network centrality"),
    "Diploma in Business Mathematics", "KIT", "Karlsruhe, Germany", "Sep. 2006 - Jul. 2012", c("Thesis: Modularity Maximization", "Implementation and comparison of different clustering algorithms using Matlab")
) %>%
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```
