---
author: Elliot Martin
title: Bioinformatician
format:
  classic-cv-pdf: default
cvcolor: 58748F #without `#`
cvfont: fetamont #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Bioinformatician
    left: SOPHiA Genetics
    right: elliotmartin92@gmail.com
  - title: Field
    left: Bioinformatics, Software Development, Data Science
    right: github.com/elliotmartin92
execute:
  echo: false
---

```{r setup}
#| warning: false
library(magrittr)
```

```{r}
#| label: cvevents
#| warning: false
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
# adds catch for lack of details to avoid empty bullet
    detail_collapse = function(details){
      if(details[1]==""){
        paste0(details, collapse = ",")
      }else{
      paste0("{", details, "}", collapse = ",")
      }
    }
    
    tbl[[details]] <- sapply(tbl[[details]], detail_collapse)
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

* Developed 15+ custom NGS pipelines for renowned hospitals and testing labs

* Aided PI to achieve over $2,000,000 in NIH grant funding by establishing bioinformatics pipelines
to facilitate the research of dozens of team-members

* Spearheaded a productive multi-year research project, managing and effectively communicating
with several team-members from different disciplines

# Education

```{r}
#| label: education
#| output: asis
#| warning: false
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Ph.D. in Biology", "University of Albany", "Albany, NY", "Aug. 2015 - Mar. 2022", c("Thesis: Post-transcriptional control underlies germline stem cell differentiation and entry into meiosis in the female Drosophila."),
    "Bachelor of Science, Biochemistry", "SUNY Geneseo", "Geneseo, NY", "Aug. 2011 - May. 2015", c("")
) %>%
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```
# Experience

```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Bioinformatician", "SOPHiA Genetics", "Apr. 2022 - Present",
    "Client Facing Bioinformatics", c("Design, release, evaluate, and document targeted gene panels and analysis pipelines to effectively identify clinically relevant genomic alterations", "Analyze and summarize various types of NGS data to clients (e.g., SNPs/INDELs, CNV, RNA fusion, and PGx alleles).
", "Communicate pipeline performance results to external clinical partners"),
    "Graduate Assistant", "University of Albany", "Aug. 2019 - Mar. 2022",
    "Biology Department", c("Established bioinformatics pipelines and scripts that are utilized by non-programmers to allow dozens of team-members to rapidly process data
", "Developed interactive browser-based tool to increase the accessibility of bulk RNA-seq and single-cell seq data",
"Discovered RNA regulatory mechanisms"),
    "QC Virology Bioinformatics Intern", "Regeneron Pharmaceuticals Inc. - Remote", "Jun. - Aug. 2020", "Regeneron Pharmaceuticals Inc.", c("Established bioinformatics pipelines for Nanopore direct RNA-seq for differential gene expression and differential isoform usage", "Developed an R Shiny application for non-bioinformaticians to process their data"),
    "Teaching Assistant", "University of Albany", "Aug. 2015 - May. 2019", "Department of Biology", c("Taught basic introductory lab skills to undergraduates and distilled principles of genetics and fostered discussions on genetics and ethics"),
) %>%
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Skills
* Programming languages: Adept in R, proficient with Bash, experience in C and Python

* Proficient with Data analysis and visualization, Linux, HPCC/Azure, Docker, Rmarkdown/Quarto, \LaTeX, version control (Git), Jira, and Gitlab

* Experienced in cell culture and related techniques such as RNAi, transfection, and viral work

* Skilled with molecular techniques including western blotting, qPCR, RNA work, and cloning

